How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-07 tse-paper/content.tex
Lines
Include 80/20
Closes #48

For each chunk retrieval technique and each project, we create
training example sets consisting of 1, 2, \dots 5 examples (lines
\circlenum{1}--\circlenum{3}).
We vary the training set size to measure how many examples we need to
confidently configure a technique, addressing \textbf{RQ2.1}.

>>>>

For each chunk retrieval technique and each project, we create
training example sets consisting of 1, 2, \dots 5 examples (lines
\circlenum{1}--\circlenum{3}).
We vary the training set size to measure how many examples we need to
confidently configure a technique, addressing \textbf{RQ2.1}. While this is atypical for an IR-based technique such as CTS---where the default is to split the whole corpus at a given percentage, often 80/20---we did this for the specific task of build logs. We want to find out how many examples one has to manually specify with a lot of effort~\Cref{sec:lit-sur:discussion} and at which point techniques become efficient.
